### 2019-03-27 latex-template/paper.tex
added intro+abstract

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Paper Title*\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
%\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
}

\maketitle

\begin{abstract}
JavaScript is the most dominant language used to develop front-ends and back-end in multiple web applications. This is because of multiple features it brings with it along the lines of event-driven and asynchronous programming; which are one of the most crucial aspects when developing a smooth and fast web interface. One of the features that helps maintain flow of instructions in asynchronous language is callbacks or higher order functions. However, a poor understanding of callbacks can result in many complexities such as nested callbacks (also referred to as callback hell). Another problem that nested callbacks can cause is lose of benefit of asynchrony since execution of program becomes linear when independent functions are nested into callbacks of other function calls. We present a tool developed in JavaScript that checks for independent instructions inside callbacks and refactors them outside of callbacks.
\end{abstract}

\begin{IEEEkeywords}
JavaScript, Callbacks, Refactoring, Asynchronous programming
\end{IEEEkeywords}

\section{1. Introduction}
Callbacks if implemented rightly can result in a very smooth and robust functioning of program, however, callbacks in JavaScript are inherently difficult to understand. They get even more complicated when there are callbacks nested within other callbacks. In addition to increasing complexity in understanding code, they can also result in loss of benefits that JavaScript brings on table with its asynchronous way of executing instructions. Consider the code excerpt in figure 1.1, we see in line number 14 a call to readfile for file1.txt with a callback, in its callback there is another call to same function with file2.txt. Execution of this code will result in a completely serial reading of files, where as we could have achieved better results if second call was outside the callback of first call.

\includegraphics[scale=0.75,read="Fig 1.1"]{introImg1.png}

On average, every tenth function in JavaScript user applications takes a callback as an argument, over 43\% of these callback functions are anonymous and majority of these callbacks are nested[ CITATION Gal15 \l 1033 ]. This naturally means, there will be many such situations where callbacks will be affecting asynchrony and their refactoring will not result in any change in execution of program. This gives us opportunity to develop a method that automates refactoring in JavaScript function callbacks in such a way that independent instructions are taken out of callbacks and placed in a scope where their earlier execution does not affect functionality of program but enhances the overall performance.
Rest of the articles is divided into following order:
3- Methodology
4- Implementation
5- Limitations and Challenges
6- Related Work
7- Conclusion

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]

\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2019-03-27 latex-template/paper.tex
added method implementation conclusion

@@
-\documentclass[conference]{IEEEtran}
+\documentclass[10pt,conference]{IEEEtran}
 \IEEEoverridecommandlockouts
@@
 }
-
 \author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
@@
 
-\section{1. Introduction}
+\section{Introduction}
 Callbacks if implemented rightly can result in a very smooth and robust functioning of program, however, callbacks in JavaScript are inherently difficult to understand.
@@
 Execution of this code will result in a completely serial reading of files, where as we could have achieved better results if second call was outside the callback of first call.
-
-\includegraphics[scale=0.75,read="Fig 1.1"]{introImg1.png}
-
+%\includegraphics[scale=0.75]{introImg1.png}
+%Figure 1.1: Example of a nested callback with independent instructions in callbacks
+%\newline
+%\newline
 On average, every tenth function in JavaScript user applications takes a callback as an argument, over 43\% of these callback functions are anonymous and majority of these callbacks are nested[ CITATION Gal15 \l 1033 ].
@@
 This gives us opportunity to develop a method that automates refactoring in JavaScript function callbacks in such a way that independent instructions are taken out of callbacks and placed in a scope where their earlier execution does not affect functionality of program but enhances the overall performance.
+
 Rest of the articles is divided into following order:
-3- Methodology
-4- Implementation
-5- Limitations and Challenges
-6- Related Work
-7- Conclusion
+\begin{itemize}
+	\item Methodology
+	\item Implementation
+	\item Limitations and Challenges
+	\item Related Work
+	\item Conclusion
 
-\section{Ease of Use}
-
-\subsection{Maintaining the Integrity of the Specifications}
-
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
-
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
-
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
-
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
-
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
 \end{itemize}
 
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
-
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
+\section{Methodology}
+Our proposed solution refactors all the independent instructions from callbacks, these can be reduced and limited to only async I/O or other blocking instruction but for simplicity we will currently refactor all independent instructions.
+Our solution mainly consists of 3 major parts:
 \begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
+	\item AST extraction
+	\item Execution context extraction
+	\item Decision based refactoring
 \end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-\begin{figure}[htbp]
-
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
-
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
+\subsection{AST extraction}
+Abstract Syntax Tree is the context form of a parse tree that contains information about order of different instructions, operators and variables.
+An AST assigns a separate node to every operator or operand it encounters in code; thus, making a full fledge tree for the whole syntax of program.
+There are multiple different tools available that produce detailed AST for any given code.
+We can extract information like names of variables, scope of variables, structure of functions and metadata like line number in actual code etc.
+\subsection{Execution Context extraction}
+Next, we use AST to develop execution context of our program.
+Execution context is the environment, different functions execute in.
+Typically, execution context contains information such as names of variables, scopes of variables, variables declared within a function and global variables.
+To extract execution context, we maintain dictionaries for different variables: for variables in scope of each function we maintain a separate dictionary, for variables declared in a function we have a separate dictionary and for arguments of function we have a different dictionary.
+We traverse the whole AST recursively from root to leaves and at each node we check if it’s a variable we append it to appropriate function’s list.
+At the end of this function we have complete execution context of the program.
+Pseudo code for Execution Context Extraction is shown in figure 2.
+\subsection{Decision based refactoring}
+After we have execution context and we know scopes of different variables, we can now make decisions about what instructions are refactorable.
+We can refactor only a few types of instruction, the fact that what instructions are fit for refactoring depends upon what variables they depend upon.
+In this perspective we can have following 4 cases:
+\begin{itemize}
+	\item {\textbf{Instruction depends upon no variable:}
+		There can be instructions that do not depend upon any of the variables for example declaration of a new variable, or line number 15 from figure 1 is fit to be refactored.
+In this case, instruction is safe to be refactored.}
+	\item{\textbf{Instruction depends upon function argument:}Since callbacks may include instructions that are dependent upon arguments of main function, we should not refactor these instructions out of function.
+Figure 3 shows another version of code from figure 1 where line 2 is not refactorable now.}
+	\item{\textbf{Instructions depend upon variables declared in scope of parent function:}
+		In this case, such an instruction will be safe to be refactored. Consult figure 4, where line number 2 is refactorable now because it has been declared in scope outside of containing function.}
+	\item{\textbf{Instruction depends on a variable declared within the scope of function:}
+		This case can have two scenarios, either the variable in terms of which the instruction is expressed is itself refactorable or it is not.
+In first case, when variable itself is refactorable, we can first let variable declaration instruction get refactored first and then refactor the instruction that contains the said variable.
+		In other case when variable cannot be refactored, we do not refactor any instruction that contains it.}
+\end{itemize}
+Now that we have mentioned decisions that will be governing decision of refactoring, we can move to actual methodology of refactoring.
+Refactoring function works recursively in bottom up manner, refactoring the deepest of callbacks first and then propagating refactoring towards the containing function.
+Figure 5 shows pseudo code for refactoring.
+For each node we recursively call refactor for every child and once all children nodes have been refactored we check for every child node with respect to fore-mentioned conditions if child node is refactorable.
+If it is refactorable, we delete that node from current tree node and add it to parent tree node.
+\section{Implementation}
+We have implemented above mentioned program in JavaScript ECMAScript 5 due to some constraints.
+We use UglifyJS to extract AST since it gives a very detailed tree with metadata such as line number and character number included within the tree.
+Additionally, it allows easy refactoring and is convertible to code even after we have made changes to tree.
+Moreover, UglifyJS also provide features such as tree compression and mangling variable names which can be helpful.
+Since UglifyJS is only compatible with JavaScript ECMAscript 5, we have also implemented our code in same version.
+\section{Limitations and Challenges}
+\section{Related Works}
+\section{Conclusion}
+Callbacks can ensure very smooth and prompt execution of program if they are implemented rightly.
+However, since callbacks tend to get complex as they get nested they might even affect asynchrony of program execution.
+Our approach tends to find such abnormalities in JavaScript programs and improves performance by refactoring such instructions to position where they are executed earlier without affecting functionality of program.
+We achieve this goal by extracting AST of code using a JavaScript library UglifyJS, next we extract execution context from the AST and finally based on this AST and few rules we choose which instructions can be refactored.
+These instructions are removed from current function’s body and are placed in callee function’s body.
+Our approach currently only works on JavaScript ECMAscript 5 due to compatibility issues of UglifyJS, but it can be extended to newer versions if replacement for UglifyJS is found.
 
@@
 \end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
 

### 2019-04-06 latex-template/paper.tex
test files + paper

@@
 email address}
-\and
-\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
 }
@@
 In addition to increasing complexity in understanding code, they can also result in loss of benefits that JavaScript brings on table with its asynchronous way of executing instructions.
-Consider the code excerpt in figure 1.1, we see in line number 14 a call to readfile for file1.txt with a callback, in its callback there is another call to same function with file2.txt.
+Consider the code excerpt in figure 1, we see in line number 14 a call to readfile for file1.txt with a callback, in its callback there is another call to same function with file2.txt.
 Execution of this code will result in a completely serial reading of files, where as we could have achieved better results if second call was outside the callback of first call.
-%\includegraphics[scale=0.75]{introImg1.png}
-%Figure 1.1: Example of a nested callback with independent instructions in callbacks
-%\newline
-%\newline
-On average, every tenth function in JavaScript user applications takes a callback as an argument, over 43\% of these callback functions are anonymous and majority of these callbacks are nested[ CITATION Gal15 \l 1033 ].
+\begin{figure}[htbp]
+	\includegraphics[scale=0.5]{introImg1.png}
+	\caption{Example of a nested callback with independent instructions in callbacks}
+	\label{fig}
+\end{figure}
+
+On average, every tenth function in JavaScript user applications takes a callback as an argument, over 43\% of these callback functions are anonymous and majority of these callbacks are nested \cite{b3}.
 This naturally means, there will be many such situations where callbacks will be affecting asynchrony and their refactoring will not result in any change in execution of program.
@@
 We can extract information like names of variables, scope of variables, structure of functions and metadata like line number in actual code etc.
+
 \subsection{Execution Context extraction}
@@
 Pseudo code for Execution Context Extraction is shown in figure 2.
+
+\begin{figure}[htbp]
+	\includegraphics[scale=0.5]{code-execcon-extract.png}
+	\caption{Pseudo code for Execution Context Extraction}
+	\label{fig}
+\end{figure}
+
 \subsection{Decision based refactoring}
@@
 In this case, instruction is safe to be refactored.}
-	\item{\textbf{Instruction depends upon function argument:}Since callbacks may include instructions that are dependent upon arguments of main function, we should not refactor these instructions out of function.
-Figure 3 shows another version of code from figure 1 where line 2 is not refactorable now.}
+	\item{\textbf{Instruction depends upon function argument:}Since callbacks may include instructions that are dependent upon arguments of main function, we should not refactor these instructions out of function.}
 	\item{\textbf{Instructions depend upon variables declared in scope of parent function:}
-		In this case, such an instruction will be safe to be refactored. Consult figure 4, where line number 2 is refactorable now because it has been declared in scope outside of containing function.}
+		In this case, such an instruction will be safe to be refactored.}
 	\item{\textbf{Instruction depends on a variable declared within the scope of function:}
@@
 \end{itemize}
+
+\begin{figure}[htbp]
+	\includegraphics[scale=0.5]{code-decision-refactor.png}
+	\caption{Pseudo code for Decision Based Refactoring}
+	\label{fig}
+\end{figure}
+
 Now that we have mentioned decisions that will be governing decision of refactoring, we can move to actual methodology of refactoring.
 Refactoring function works recursively in bottom up manner, refactoring the deepest of callbacks first and then propagating refactoring towards the containing function.
-Figure 5 shows pseudo code for refactoring.
+Figure 3 shows pseudo code for refactoring.
 For each node we recursively call refactor for every child and once all children nodes have been refactored we check for every child node with respect to fore-mentioned conditions if child node is refactorable.
@@
 Since UglifyJS is only compatible with JavaScript ECMAscript 5, we have also implemented our code in same version.
+
+\section{Testing}
 \section{Limitations and Challenges}
 \section{Related Works}
+Not a lot of work have been done regarding this specific problem. Following few pieces of work have some indirect relations with our work. 
+\begin{itemize}
+	\item {\textbf{Classification of Callbacks:}
+		This paper does in depth analysis of 138 JavaScript pages with over 5 million 
+		lines of codes.
+Study shows that around every 10th function takes a callback as an argument and 43\% of these callbacks are anonymous functions.
+Among these functions almost half are asynchronous calls.
+This shows importance of a tool that polices callbacks to ensure callbacks do not become too complicated \cite{b3}.
+	}
+	\item{\textbf{Synchronous to Asynchronous:}
+		Realizing the importance and usefulness of asynchronous programming, this work introduces way to convert to synchronous code of JavaScript to asynchronous to improve responsiveness of mobile apps \cite{b1}.
+	}
+	\item{\textbf{Detecting JS code smells:}
+		This paper does analysis of a sample of JavaScript programs and finds most common coding flaws.
+It presents a way of detecting these code smells.
+A notable code smell it talks about is nested callbacks, which can become hard to read and consequently debug.
+However, it only detects these code smells and does not provide any solution.
+Our work extends on this explicit problem and we try to cover a subset of problems caused by callbacks and try to solve \cite{b2}.
+	}
+\end{itemize}
 \section{Conclusion}
@@
 \begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
+\bibitem{b1} D. Dig ``Refactoring for asynchronous execution on mobile'' in IEEE Software, 2015.
+\bibitem{b2} A.M. Fard and A. Mesbah "JSNOSE: detecting javaScript code smells" in IEEE 13th International Working Conference on Source Code Analysis and Manipulation (SCAM), 2013.
+\bibitem{b3} G. Keheliya, A. Mesbah and B. Ivan "Don't call us, we'll call you: characterizing callbacks in javascript" in IEEE Empirical Software Engineering and Measurement (ESEM), 2015.
 \end{thebibliography}

### 2019-04-06 code/test.js

@@ -1,23 +1,0 @@
-var fs = require('fs');
-
-var readfile = function(name,cb){
-	fs.readFile(file, "utf-8", function (err, data) {
-		cb(data)
-	})
-}
-
-
-var fname = "a.txt"
-var fname2 = "b.txt"
-var fname3 = "ab.txt"
-readfile(fname, function(data){
-	console.log(fname2)
-	readfile(fname2, function(data2){
-		console.log(fname3)
-		readfile(fname3, function(data3){
-			console.log(data)
-			console.log(data2)
-			console.log(data3)
-		})
-	})
-})

### 2019-04-06 code/test1.js

@@ -1,52 +1,0 @@
-var fs = require('fs')
-
-var readfile = function(name,cb){
-	fs.readFile(file, "utf-8", function (err, data) {
-		cb(data)
-	})
-}
-
-var writefile = function(file,data,cb){
-	fs.writeFile(file,data,function(err){
-		cb(err);
-	})
-}
-
-var list_of_files = ['a.txt','b.txt','c.txt']
-
-var To_Upper_Case = function(data){
-	return data.toUpperCase()
-}
-
-var readfiles_from_list = function(list){
-	list.forEach(function (i){
-		readfile(i, function(data){
-			var first_file = data[0]
-			var second_file = data[1]
-			var third_file = data[2]
-			readfile(first_file, function(d1){
-				readfile(second_file, function(d2){
-					readfile(third_file, function(d3){
-						var n_first = To_Upper_Case(first_file)
-						var n_snd = To_Upper_Case(second_file)
-						var n_thrd = To_Upper_Case(third_file)
-						console.log(n_first,d1)
-						console.log(n_snd,d2)
-						console.log(n_thrd,d3)
-						writefile(first_file,d1,function(e1){
-							console.log(e1)
-						})
-						writefile(second_file,d2,function(e2){
-							console.log(e2)
-						})
-						writefile(third_file,d3,function(e3){
-							console.log(e3)
-						})
-					})
-				})
-			})
-		})
-	})
-}
-
-readfiles_from_list(list_of_files);

### 2019-04-06 code/test2.js

@@ -1,43 +1,0 @@
-var fs = require('fs');
-
-var readfile = function(file, cb) {
-	fs.readFile(file, "utf-8", function (err, data) {
-		console.log("data");
-		var datal = data.length;
-		console.log(datal)
-	});
-	cb('done');
-};
-
-var fact = function fact(n) {
-	if (n < 1) {
-		var q = n-1;
-		return 1;
-	}
-	return n * fact(n - 1);
-};
-
-
-var nfunc = function() {
-	var file = "test.txt";
-	var n = "ajhsjahd";
-	n = n-n+n;
-	readfile(file, function (data) {
-	console.log(n.length);
-	console.log(data);
-	});
-	for(var i=0; i<data.length; i++){
-		var k = 0;
-		console.log(data[i]);
-	}
-	var g=9;
-	while(g>0){
-		g--;
-	}
-	list = [1,2,3]
-	list.forEach(function(i){
-		i++;
-	})
-}
-
-nfunc()

### 2019-04-06 test-data/es5/test.js

@@ -1,0 +1,22 @@
+var fs = require('fs');
+
+var readfile = function (name, cb) {
+  fs.readFile(file, "utf-8", function (err, data) {
+    cb(data);
+  });
+};
+
+var fname = "a.txt";
+var fname2 = "b.txt";
+var fname3 = "ab.txt";
+readfile(fname, function (data) {
+  console.log(fname2);
+  readfile(fname2, function (data2) {
+    console.log(fname3);
+    readfile(fname3, function (data3) {
+      console.log(data);
+      console.log(data2);
+      console.log(data3);
+    });
+  });
+});

### 2019-04-06 test-data/es5/test1.js

@@ -1,0 +1,52 @@
+var fs = require('fs');
+
+var readfile = function (name, cb) {
+  fs.readFile(file, "utf-8", function (err, data) {
+    cb(data);
+  });
+};
+
+var writefile = function (file, data, cb) {
+  fs.writeFile(file, data, function (err) {
+    cb(err);
+  });
+};
+
+var list_of_files = ['a.txt', 'b.txt', 'c.txt'];
+
+var To_Upper_Case = function (data) {
+  return data.toUpperCase();
+};
+
+var readfiles_from_list = function (list) {
+  list.forEach(function (i) {
+    readfile(i, function (data) {
+      var first_file = data[0];
+      var second_file = data[1];
+      var third_file = data[2];
+      readfile(first_file, function (d1) {
+        readfile(second_file, function (d2) {
+          readfile(third_file, function (d3) {
+            var n_first = To_Upper_Case(first_file);
+            var n_snd = To_Upper_Case(second_file);
+            var n_thrd = To_Upper_Case(third_file);
+            console.log(n_first, d1);
+            console.log(n_snd, d2);
+            console.log(n_thrd, d3);
+            writefile(first_file, d1, function (e1) {
+              console.log(e1);
+            });
+            writefile(second_file, d2, function (e2) {
+              console.log(e2);
+            });
+            writefile(third_file, d3, function (e3) {
+              console.log(e3);
+            });
+          });
+        });
+      });
+    });
+  });
+};
+
+readfiles_from_list(list_of_files);

### 2019-04-06 test-data/es5/test2.js

@@ -1,0 +1,47 @@
+var fs = require('fs');
+
+var readfile = function (file, cb) {
+  fs.readFile(file, "utf-8", function (err, data) {
+    console.log("data");
+    var datal = data.length;
+    console.log(datal);
+  });
+  cb('done');
+};
+
+var fact = function fact(n) {
+  if (n < 1) {
+    var q = n - 1;
+    return 1;
+  }
+
+  return n * fact(n - 1);
+};
+
+var nfunc = function () {
+  var file = "test.txt";
+  var n = "ajhsjahd";
+  n = n - n + n;
+  readfile(file, function (data) {
+    console.log(n.length);
+    console.log(data);
+  });
+
+  for (var i = 0; i < data.length; i++) {
+    var k = 0;
+    console.log(data[i]);
+  }
+
+  var g = 9;
+
+  while (g > 0) {
+    g--;
+  }
+
+  list = [1, 2, 3];
+  list.forEach(function (i) {
+    i++;
+  });
+};
+
+nfunc();

### 2019-04-06 test-data/orig/jshttp-compressible-test.js

@@ -1,0 +1,84 @@
+// file taken from https://github.com/jshttp/compressible/blob/master/test/test.js
+
+var assert = require('assert')
+var db = require('mime-db')
+var compressible = require('../')
+
+// None of these should be actual types so that the lookup will never include them.
+var EXAMPLE_TYPES = [
+  { type: 'text/penguins', should: true },
+  { type: 'text/html', should: true },
+  { type: 'text/plain', should: true },
+  { type: 'text/jade', should: true },
+  { type: 'something/text', should: undefined },
+  { type: 'something/frog+TEXT', should: true },
+  { type: 'type/json;askjkl+json', should: undefined },
+  { type: 'type/+json', should: true },
+  { type: 'data/beans+xml ; charset="utf-8"', should: true },
+  { type: 'can/worms+xml;blaaaah', should: true },
+  { type: 'data/xml', should: undefined },
+  { type: 'asdf/nope', should: undefined },
+  { type: 'cats', should: undefined }
+]
+
+var INVALID_TYPES = [
+  undefined,
+  null,
+  0,
+  1,
+  false,
+  true
+]
+
+describe('Testing if spec lookups are correct.', function () {
+  it('All DB `compressible` types should reflect in compressible', function () {
+    for (var type in db) {
+      if (db[type].compressible !== undefined) {
+        assert.strictEqual(compressible(type), db[type].compressible)
+      }
+    }
+  })
+})
+
+describe('Testing if the regex works as intended.', function () {
+  EXAMPLE_TYPES.forEach(function (example) {
+    it(example.type + ' should' + (example.should ? ' ' : ' not ') + 'be compressible', function () {
+      assert.strictEqual(compressible(example.type), example.should)
+    })
+  })
+})
+
+describe('Testing if charsets are handled correctly.', function () {
+  it('Charsets should be stripped off without issue', function () {
+    for (var type in db) {
+      if (db[type].compressible !== undefined) {
+        assert.strictEqual(compressible(type + '; charset=utf-8'), db[type].compressible)
+      }
+    }
+  })
+})
+
+describe('Ensuring invalid types do not cause errors.', function () {
+  it('No arguments should return false without error', function () {
+    assert.strictEqual(compressible(), false)
+  })
+
+  INVALID_TYPES.forEach(function (invalid) {
+    it(invalid + ' should return false without error', function () {
+      assert.doesNotThrow(function () {
[…]

### 2019-04-06 test-data/orig/jshttp-on-finished-test.js

@@ -1,0 +1,1080 @@
+// file taken from https://github.com/jshttp/on-finished/blob/master/test/test.js
+
+var assert = require('assert')
+var http = require('http')
+var net = require('net')
+var onFinished = require('..')
+
+describe('onFinished(res, listener)', function () {
+  it('should invoke listener given an unknown object', function (done) {
+    onFinished({}, done)
+  })
+
+  describe('when the response finishes', function () {
+    it('should fire the callback', function (done) {
+      var server = http.createServer(function (req, res) {
+        onFinished(res, done)
+        setTimeout(res.end.bind(res), 0)
+      })
+
+      sendGet(server)
+    })
+
+    it('should include the response object', function (done) {
+      var server = http.createServer(function (req, res) {
+        onFinished(res, function (err, msg) {
+          assert.ok(!err)
+          assert.strictEqual(msg, res)
+          done()
+        })
+        setTimeout(res.end.bind(res), 0)
+      })
+
+      sendGet(server)
+    })
+
+    it('should fire when called after finish', function (done) {
+      var server = http.createServer(function (req, res) {
+        onFinished(res, function () {
+          onFinished(res, done)
+        })
+        setTimeout(res.end.bind(res), 0)
+      })
+
+      sendGet(server)
+    })
+  })
+
+  describe('when using keep-alive', function () {
+    it('should fire for each response', function (done) {
+      var called = false
+      var server = http.createServer(function (req, res) {
+        onFinished(res, function () {
+          if (called) {
+            socket.end()
+            server.close()
+            done(called !== req ? null : new Error('fired twice on same req'))
+            return
+          }
+
+          called = req
+
+          writeRequest(socket)
+        })
+
+        res.end()
+      })
+      var socket
+
+      server.listen(function () {
+        socket = net.connect(this.address().port, function () {
+          writeRequest(this)
+        })
+      })
+    })
+  })
+
+  describe('when requests pipelined', function () {
+    it('should fire for each request', function (done) {
+      var count = 0
+      var responses = []
+      var server = http.createServer(function (req, res) {
+        responses.push(res)
+
+        onFinished(res, function (err) {
+          assert.ifError(err)
+          assert.strictEqual(responses[0], res)
+          responses.shift()
+
+          if (responses.length === 0) {
+            socket.end()
+            return
+          }
+
+          responses[0].end('response b')
+        })
+
+        onFinished(req, function (err) {
+          assert.ifError(err)
+
[…]

### 2019-04-06 test-data/orig/jshttp-on-headers-test.js

@@ -1,0 +1,313 @@
+// file taken from https://github.com/jshttp/on-headers/blob/master/test/test.js
+
+var assert = require('assert')
+var http = require('http')
+var onHeaders = require('..')
+var request = require('supertest')
+
+describe('onHeaders(res, listener)', function () {
+  it('should fire after setHeader', function (done) {
+    var server = createServer(echoListener)
+
+    request(server)
+      .get('/')
+      .expect('X-Outgoing-Echo', 'test')
+      .expect(200, done)
+  })
+
+  it('should fire before write', function (done) {
+    var server = createServer(echoListener, handler)
+
+    function handler (req, res) {
+      res.setHeader('X-Outgoing', 'test')
+      res.write('1')
+    }
+
+    request(server)
+      .get('/')
+      .expect('X-Outgoing-Echo', 'test')
+      .expect(200, '1', done)
+  })
+
+  it('should fire with no headers', function (done) {
+    var server = createServer(listener, handler)
+
+    function handler (req, res) {}
+
+    function listener (req, res) {
+      this.setHeader('X-Headers', Object.keys(this._headers || {}).join(','))
+    }
+
+    request(server)
+      .get('/')
+      .expect('X-Headers', '')
+      .expect(200, done)
+  })
+
+  it('should fire only once', function (done) {
+    var count = 0
+    var server = createServer(listener, handler)
+
+    function handler (req, res) {
+      res.writeHead(200)
+
+      try { res.writeHead(200) } catch (e) {}
+    }
+
+    function listener (req, res) {
+      count++
+    }
+
+    request(server)
+      .get('/')
+      .expect(200, function (err) {
+        if (err) return done(err)
+        assert.strictEqual(count, 1)
+        done()
+      })
+  })
+
+  it('should fire in reverse order', function (done) {
+    var server = createServer(echoListener, handler)
+
+    function handler (req, res) {
+      onHeaders(res, appendHeader(1))
+      onHeaders(res, appendHeader(2))
+      onHeaders(res, appendHeader(3))
+      res.setHeader('X-Outgoing', 'test')
+    }
+
+    request(server)
+      .get('/')
+      .expect('X-Outgoing-Echo', 'test,3,2,1')
+      .expect(200, done)
+  })
+
+  describe('arguments', function () {
+    describe('res', function () {
+      it('should be required', function () {
+        assert.throws(onHeaders.bind(), /res.*required/)
+      })
+    })
+
+    describe('listener', function () {
[…]

### 2019-04-06 test-data/orig/jshttp-proxy-addr-test.js

@@ -1,0 +1,513 @@
+// file taken from https://github.com/jshttp/proxy-addr/blob/master/test/test.js
+
+var assert = require('assert')
+var proxyaddr = require('..')
+
+describe('proxyaddr(req, trust)', function () {
+  describe('arguments', function () {
+    describe('req', function () {
+      it('should be required', function () {
+        assert.throws(proxyaddr, /req.*required/)
+      })
+    })
+
+    describe('trust', function () {
+      it('should be required', function () {
+        var req = createReq('127.0.0.1')
+        assert.throws(proxyaddr.bind(null, req), /trust.*required/)
+      })
+
+      it('should accept a function', function () {
+        var req = createReq('127.0.0.1')
+        assert.doesNotThrow(proxyaddr.bind(null, req, all))
+      })
+
+      it('should accept an array', function () {
+        var req = createReq('127.0.0.1')
+        assert.doesNotThrow(proxyaddr.bind(null, req, []))
+      })
+
+      it('should accept a string', function () {
+        var req = createReq('127.0.0.1')
+        assert.doesNotThrow(proxyaddr.bind(null, req, '127.0.0.1'))
+      })
+
+      it('should reject a number', function () {
+        var req = createReq('127.0.0.1')
+        assert.throws(proxyaddr.bind(null, req, 42), /unsupported trust argument/)
+      })
+
+      it('should accept IPv4', function () {
+        var req = createReq('127.0.0.1')
+        assert.doesNotThrow(proxyaddr.bind(null, req, '127.0.0.1'))
+      })
+
+      it('should accept IPv6', function () {
+        var req = createReq('127.0.0.1')
+        assert.doesNotThrow(proxyaddr.bind(null, req, '::1'))
+      })
+
+      it('should accept IPv4-style IPv6', function () {
+        var req = createReq('127.0.0.1')
+        assert.doesNotThrow(proxyaddr.bind(null, req, '::ffff:127.0.0.1'))
+      })
+
+      it('should accept pre-defined names', function () {
+        var req = createReq('127.0.0.1')
+        assert.doesNotThrow(proxyaddr.bind(null, req, 'loopback'))
+      })
+
+      it('should accept pre-defined names in array', function () {
+        var req = createReq('127.0.0.1')
[…]

### 2019-04-06 test-data/orig/npm-cli-nodemods-lockfile.js

@@ -1,0 +1,322 @@
+// file taken from https://github.com/npm/cli/blob/latest/node_modules/lockfile/lockfile.js
+
+var fs = require('fs')
+
+var wx = 'wx'
+if (process.version.match(/^v0\.[0-6]/)) {
+  var c = require('constants')
+  wx = c.O_TRUNC | c.O_CREAT | c.O_WRONLY | c.O_EXCL
+}
+
+var os = require('os')
+exports.filetime = 'ctime'
+if (os.platform() == "win32") {
+  exports.filetime = 'mtime'
+}
+
+var debug
+var util = require('util')
+if (util.debuglog)
+  debug = util.debuglog('LOCKFILE')
+else if (/\blockfile\b/i.test(process.env.NODE_DEBUG))
+  debug = function() {
+    var msg = util.format.apply(util, arguments)
+    console.error('LOCKFILE %d %s', process.pid, msg)
+  }
+else
+  debug = function() {}
+
+var locks = {}
+
+function hasOwnProperty (obj, prop) {
+  return Object.prototype.hasOwnProperty.call(obj, prop)
+}
+
+var onExit = require('signal-exit')
+onExit(function () {
+  debug('exit listener')
+  // cleanup
+  Object.keys(locks).forEach(exports.unlockSync)
+})
+
+// XXX https://github.com/joyent/node/issues/3555
+// Remove when node 0.8 is deprecated.
+if (/^v0\.[0-8]\./.test(process.version)) {
+  debug('uncaughtException, version = %s', process.version)
+  process.on('uncaughtException', function H (er) {
+    debug('uncaughtException')
+    var l = process.listeners('uncaughtException').filter(function (h) {
+      return h !== H
+    })
+    if (!l.length) {
+      // cleanup
+      try { Object.keys(locks).forEach(exports.unlockSync) } catch (e) {}
+      process.removeListener('uncaughtException', H)
+      throw er
+    }
+  })
+}
+
+exports.unlock = function (path, cb) {
+  debug('unlock', path)
+  // best-effort.  unlocking an already-unlocked lock is a noop
+  delete locks[path]
+  fs.unlink(path, function (unlinkEr) { cb && cb() })
+}
+
+exports.unlockSync = function (path) {
+  debug('unlockSync', path)
+  // best-effort.  unlocking an already-unlocked lock is a noop
+  try { fs.unlinkSync(path) } catch (er) {}
+  delete locks[path]
+}
+
+
+// if the file can be opened in readonly mode, then it's there.
[…]

### 2019-04-06 test-data/orig/npm-npm-expansions-build.js

@@ -1,0 +1,34 @@
+// file taken from https://github.com/npm/npm-expansions/blob/master/build.js
+
+var fs       = require("fs")
+var infile   = __dirname + '/expansions.txt'
+var outfile_pre  = __dirname + '/expansions'
+var outfile_json = outfile_pre + '.json'
+var outfile_txt = outfile_pre + '.txt'
+
+var list = fs
+  .readFileSync(infile, 'utf8')
+  .split("\n")
+  .map(function(e) { return e.trim() })
+  .filter(function(e) { return (e.length > 0) })
+  .filter(function(e) { return e.charAt(0) !== '#' })
+  .sort(function (a, b) {
+    return a.toLowerCase().localeCompare(b.toLowerCase());
+  })
+
+fs.writeFileSync(outfile_json, JSON.stringify(list, null, 2))
+
+fs.writeFileSync(outfile_txt, list.reduce(
+  function(p, c){
+    return p + c + '\n'
+  }, list.shift() + '\n')
+)
+// reappend the instructions
+fs.appendFileSync(
+  outfile_txt,
+  "#\n" +
+  "# please don't add your expansions down here!\n" +
+  "# insert them in alphabetical order to help reduce merge conflicts.\n" +
+  "#\n" +
+  "# <3\n"
+)

### 2019-04-06 test-data/orig/test.js

@@ -1,0 +1,23 @@
+var fs = require('fs');
+
+var readfile = function(name,cb){
+	fs.readFile(file, "utf-8", function (err, data) {
+		cb(data)
+	})
+}
+
+
+var fname = "a.txt"
+var fname2 = "b.txt"
+var fname3 = "ab.txt"
+readfile(fname, function(data){
+	console.log(fname2)
+	readfile(fname2, function(data2){
+		console.log(fname3)
+		readfile(fname3, function(data3){
+			console.log(data)
+			console.log(data2)
+			console.log(data3)
+		})
+	})
+})

### 2019-04-06 test-data/orig/test1.js

@@ -1,0 +1,52 @@
+var fs = require('fs')
+
+var readfile = function(name,cb){
+	fs.readFile(file, "utf-8", function (err, data) {
+		cb(data)
+	})
+}
+
+var writefile = function(file,data,cb){
+	fs.writeFile(file,data,function(err){
+		cb(err);
+	})
+}
+
+var list_of_files = ['a.txt','b.txt','c.txt']
+
+var To_Upper_Case = function(data){
+	return data.toUpperCase()
+}
+
+var readfiles_from_list = function(list){
+	list.forEach(function (i){
+		readfile(i, function(data){
+			var first_file = data[0]
+			var second_file = data[1]
+			var third_file = data[2]
+			readfile(first_file, function(d1){
+				readfile(second_file, function(d2){
+					readfile(third_file, function(d3){
+						var n_first = To_Upper_Case(first_file)
+						var n_snd = To_Upper_Case(second_file)
+						var n_thrd = To_Upper_Case(third_file)
+						console.log(n_first,d1)
+						console.log(n_snd,d2)
+						console.log(n_thrd,d3)
+						writefile(first_file,d1,function(e1){
+							console.log(e1)
+						})
+						writefile(second_file,d2,function(e2){
+							console.log(e2)
+						})
+						writefile(third_file,d3,function(e3){
+							console.log(e3)
+						})
+					})
+				})
+			})
+		})
+	})
+}
+
+readfiles_from_list(list_of_files);

### 2019-04-06 test-data/tester.py

@@ -1,0 +1,13 @@
+import glob
+import os
+
+os.system('npm run convert-es5')
+
+files = glob.glob('es5/*.js')
+
+for i in files:
+	fname = i.split('/')[1].split('.')[0] +'.JSON'
+	os.system('uglifyjs --output ast '+i+' > asts/'+fname)
+
+print(len(files), 'files converted to ast')
+

### 2019-04-06 test-data/es5/jshttp-compressible-test.js
testing, handle error in npm/cli file

@@ -1,0 +1,95 @@
+// file taken from https://github.com/jshttp/compressible/blob/master/test/test.js
+var assert = require('assert');
+
+var db = require('mime-db');
+
+var compressible = require('../'); // None of these should be actual types so that the lookup will never include them.
+
+
+var EXAMPLE_TYPES = [{
+  type: 'text/penguins',
+  should: true
+}, {
+  type: 'text/html',
+  should: true
+}, {
+  type: 'text/plain',
+  should: true
+}, {
+  type: 'text/jade',
+  should: true
+}, {
+  type: 'something/text',
+  should: undefined
+}, {
+  type: 'something/frog+TEXT',
+  should: true
+}, {
+  type: 'type/json;askjkl+json',
+  should: undefined
+}, {
+  type: 'type/+json',
+  should: true
+}, {
+  type: 'data/beans+xml ; charset="utf-8"',
+  should: true
+}, {
+  type: 'can/worms+xml;blaaaah',
+  should: true
+}, {
+  type: 'data/xml',
+  should: undefined
+}, {
+  type: 'asdf/nope',
+  should: undefined
+}, {
+  type: 'cats',
+  should: undefined
+}];
+var INVALID_TYPES = [undefined, null, 0, 1, false, true];
+describe('Testing if spec lookups are correct.', function () {
+  it('All DB `compressible` types should reflect in compressible', function () {
+    for (var type in db) {
+      if (db[type].compressible !== undefined) {
+        assert.strictEqual(compressible(type), db[type].compressible);
+      }
+    }
+  });
+});
+describe('Testing if the regex works as intended.', function () {
+  EXAMPLE_TYPES.forEach(function (example) {
+    it(example.type + ' should' + (example.should ? ' ' : ' not ') + 'be compressible', function () {
+      assert.strictEqual(compressible(example.type), example.should);
+    });
+  });
+});
+describe('Testing if charsets are handled correctly.', function () {
+  it('Charsets should be stripped off without issue', function () {
+    for (var type in db) {
+      if (db[type].compressible !== undefined) {
+        assert.strictEqual(compressible(type + '; charset=utf-8'), db[type].compressible);
+      }
+    }
+  });
+});
+describe('Ensuring invalid types do not cause errors.', function () {
+  it('No arguments should return false without error', function () {
+    assert.strictEqual(compressible(), false);
+  });
+  INVALID_TYPES.forEach(function (invalid) {
+    it(invalid + ' should return false without error', function () {
[…]

### 2019-04-06 test-data/es5/jshttp-on-finished-test.js

@@ -1,0 +1,956 @@
+// file taken from https://github.com/jshttp/on-finished/blob/master/test/test.js
+var assert = require('assert');
+
+var http = require('http');
+
+var net = require('net');
+
+var onFinished = require('..');
+
+describe('onFinished(res, listener)', function () {
+  it('should invoke listener given an unknown object', function (done) {
+    onFinished({}, done);
+  });
+  describe('when the response finishes', function () {
+    it('should fire the callback', function (done) {
+      var server = http.createServer(function (req, res) {
+        onFinished(res, done);
+        setTimeout(res.end.bind(res), 0);
+      });
+      sendGet(server);
+    });
+    it('should include the response object', function (done) {
+      var server = http.createServer(function (req, res) {
+        onFinished(res, function (err, msg) {
+          assert.ok(!err);
+          assert.strictEqual(msg, res);
+          done();
+        });
+        setTimeout(res.end.bind(res), 0);
+      });
+      sendGet(server);
+    });
+    it('should fire when called after finish', function (done) {
+      var server = http.createServer(function (req, res) {
+        onFinished(res, function () {
+          onFinished(res, done);
+        });
+        setTimeout(res.end.bind(res), 0);
+      });
+      sendGet(server);
+    });
+  });
+  describe('when using keep-alive', function () {
+    it('should fire for each response', function (done) {
+      var called = false;
+      var server = http.createServer(function (req, res) {
+        onFinished(res, function () {
+          if (called) {
+            socket.end();
+            server.close();
+            done(called !== req ? null : new Error('fired twice on same req'));
+            return;
+          }
+
+          called = req;
+          writeRequest(socket);
+        });
+        res.end();
+      });
+      var socket;
+      server.listen(function () {
+        socket = net.connect(this.address().port, function () {
+          writeRequest(this);
+        });
+      });
+    });
+  });
+  describe('when requests pipelined', function () {
+    it('should fire for each request', function (done) {
+      var count = 0;
+      var responses = [];
+      var server = http.createServer(function (req, res) {
+        responses.push(res);
+        onFinished(res, function (err) {
+          assert.ifError(err);
+          assert.strictEqual(responses[0], res);
+          responses.shift();
+
+          if (responses.length === 0) {
+            socket.end();
+            return;
+          }
+
+          responses[0].end('response b');
+        });
+        onFinished(req, function (err) {
+          assert.ifError(err);
+
+          if (++count !== 2) {
+            return;
+          }
+
[…]

### 2019-04-06 test-data/es5/jshttp-on-headers-test.js

@@ -1,0 +1,250 @@
+// file taken from https://github.com/jshttp/on-headers/blob/master/test/test.js
+var assert = require('assert');
+
+var http = require('http');
+
+var onHeaders = require('..');
+
+var request = require('supertest');
+
+describe('onHeaders(res, listener)', function () {
+  it('should fire after setHeader', function (done) {
+    var server = createServer(echoListener);
+    request(server).get('/').expect('X-Outgoing-Echo', 'test').expect(200, done);
+  });
+  it('should fire before write', function (done) {
+    var server = createServer(echoListener, handler);
+
+    function handler(req, res) {
+      res.setHeader('X-Outgoing', 'test');
+      res.write('1');
+    }
+
+    request(server).get('/').expect('X-Outgoing-Echo', 'test').expect(200, '1', done);
+  });
+  it('should fire with no headers', function (done) {
+    var server = createServer(listener, handler);
+
+    function handler(req, res) {}
+
+    function listener(req, res) {
+      this.setHeader('X-Headers', Object.keys(this._headers || {}).join(','));
+    }
+
+    request(server).get('/').expect('X-Headers', '').expect(200, done);
+  });
+  it('should fire only once', function (done) {
+    var count = 0;
+    var server = createServer(listener, handler);
+
+    function handler(req, res) {
+      res.writeHead(200);
+
+      try {
+        res.writeHead(200);
+      } catch (e) {}
+    }
+
+    function listener(req, res) {
+      count++;
+    }
+
+    request(server).get('/').expect(200, function (err) {
+      if (err) return done(err);
+      assert.strictEqual(count, 1);
+      done();
+    });
+  });
+  it('should fire in reverse order', function (done) {
+    var server = createServer(echoListener, handler);
+
+    function handler(req, res) {
+      onHeaders(res, appendHeader(1));
+      onHeaders(res, appendHeader(2));
+      onHeaders(res, appendHeader(3));
+      res.setHeader('X-Outgoing', 'test');
+    }
+
+    request(server).get('/').expect('X-Outgoing-Echo', 'test,3,2,1').expect(200, done);
+  });
+  describe('arguments', function () {
+    describe('res', function () {
+      it('should be required', function () {
+        assert.throws(onHeaders.bind(), /res.*required/);
+      });
+    });
+    describe('listener', function () {
+      it('should be required', function (done) {
+        var server = createServer();
+        request(server).get('/').expect(500, /listener.*function/, done);
+      });
[…]

### 2019-04-06 test-data/es5/jshttp-proxy-addr-test.js

@@ -1,0 +1,441 @@
+// file taken from https://github.com/jshttp/proxy-addr/blob/master/test/test.js
+var assert = require('assert');
+
+var proxyaddr = require('..');
+
+describe('proxyaddr(req, trust)', function () {
+  describe('arguments', function () {
+    describe('req', function () {
+      it('should be required', function () {
+        assert.throws(proxyaddr, /req.*required/);
+      });
+    });
+    describe('trust', function () {
+      it('should be required', function () {
+        var req = createReq('127.0.0.1');
+        assert.throws(proxyaddr.bind(null, req), /trust.*required/);
+      });
+      it('should accept a function', function () {
+        var req = createReq('127.0.0.1');
+        assert.doesNotThrow(proxyaddr.bind(null, req, all));
+      });
+      it('should accept an array', function () {
+        var req = createReq('127.0.0.1');
+        assert.doesNotThrow(proxyaddr.bind(null, req, []));
+      });
+      it('should accept a string', function () {
+        var req = createReq('127.0.0.1');
+        assert.doesNotThrow(proxyaddr.bind(null, req, '127.0.0.1'));
+      });
+      it('should reject a number', function () {
+        var req = createReq('127.0.0.1');
+        assert.throws(proxyaddr.bind(null, req, 42), /unsupported trust argument/);
+      });
+      it('should accept IPv4', function () {
+        var req = createReq('127.0.0.1');
+        assert.doesNotThrow(proxyaddr.bind(null, req, '127.0.0.1'));
+      });
+      it('should accept IPv6', function () {
+        var req = createReq('127.0.0.1');
+        assert.doesNotThrow(proxyaddr.bind(null, req, '::1'));
+      });
+      it('should accept IPv4-style IPv6', function () {
+        var req = createReq('127.0.0.1');
+        assert.doesNotThrow(proxyaddr.bind(null, req, '::ffff:127.0.0.1'));
+      });
+      it('should accept pre-defined names', function () {
+        var req = createReq('127.0.0.1');
+        assert.doesNotThrow(proxyaddr.bind(null, req, 'loopback'));
+      });
+      it('should accept pre-defined names in array', function () {
+        var req = createReq('127.0.0.1');
[…]

### 2019-04-06 test-data/es5/npm-cli-nodemods-lockfile.js

@@ -1,0 +1,334 @@
+// file taken from https://github.com/npm/cli/blob/latest/node_modules/lockfile/lockfile.js
+var fs = require('fs');
+
+var wx = 'wx';
+
+if (process.version.match(/^v0\.[0-6]/)) {
+  var c = require('constants');
+
+  wx = c.O_TRUNC | c.O_CREAT | c.O_WRONLY | c.O_EXCL;
+}
+
+var os = require('os');
+
+exports.filetime = 'ctime';
+
+if (os.platform() == "win32") {
+  exports.filetime = 'mtime';
+}
+
+var debug;
+
+var util = require('util');
+
+if (util.debuglog) debug = util.debuglog('LOCKFILE');else if (/\blockfile\b/i.test(process.env.NODE_DEBUG)) debug = function () {
+  var msg = util.format.apply(util, arguments);
+  console.error('LOCKFILE %d %s', process.pid, msg);
+};else debug = function () {};
+var locks = {};
+
+function hasOwnProperty(obj, prop) {
+  return Object.prototype.hasOwnProperty.call(obj, prop);
+}
+
+var onExit = require('signal-exit');
+
+onExit(function () {
+  debug('exit listener'); // cleanup
+
+  Object.keys(locks).forEach(exports.unlockSync);
+}); // XXX https://github.com/joyent/node/issues/3555
+// Remove when node 0.8 is deprecated.
+
+if (/^v0\.[0-8]\./.test(process.version)) {
+  debug('uncaughtException, version = %s', process.version);
+  process.on('uncaughtException', function H(er) {
+    debug('uncaughtException');
+    var l = process.listeners('uncaughtException').filter(function (h) {
+      return h !== H;
+    });
+
+    if (!l.length) {
+      // cleanup
+      try {
+        Object.keys(locks).forEach(exports.unlockSync);
+      } catch (e) {}
+
+      process.removeListener('uncaughtException', H);
+      throw er;
+    }
+  });
+}
+
+exports.unlock = function (path, cb) {
+  debug('unlock', path); // best-effort.  unlocking an already-unlocked lock is a noop
+
+  delete locks[path];
+  fs.unlink(path, function (unlinkEr) {
+    cb && cb();
+  });
+};
+
+exports.unlockSync = function (path) {
+  debug('unlockSync', path); // best-effort.  unlocking an already-unlocked lock is a noop
+
+  try {
+    fs.unlinkSync(path);
+  } catch (er) {}
+
[…]

### 2019-04-06 test-data/es5/npm-npm-expansions-build.js

@@ -1,0 +1,22 @@
+// file taken from https://github.com/npm/npm-expansions/blob/master/build.js
+var fs = require("fs");
+
+var infile = __dirname + '/expansions.txt';
+var outfile_pre = __dirname + '/expansions';
+var outfile_json = outfile_pre + '.json';
+var outfile_txt = outfile_pre + '.txt';
+var list = fs.readFileSync(infile, 'utf8').split("\n").map(function (e) {
+  return e.trim();
+}).filter(function (e) {
+  return e.length > 0;
+}).filter(function (e) {
+  return e.charAt(0) !== '#';
+}).sort(function (a, b) {
+  return a.toLowerCase().localeCompare(b.toLowerCase());
+});
+fs.writeFileSync(outfile_json, JSON.stringify(list, null, 2));
+fs.writeFileSync(outfile_txt, list.reduce(function (p, c) {
+  return p + c + '\n';
+}, list.shift() + '\n')); // reappend the instructions
+
+fs.appendFileSync(outfile_txt, "#\n" + "# please don't add your expansions down here!\n" + "# insert them in alphabetical order to help reduce merge conflicts.\n" + "#\n" + "# <3\n");

### 2019-05-06 code/refactorJS.js
numbers patch

@@ -41,23 +41,20 @@ async function convertAstToCode(ast){
 	return uglifyjs.minify(ast, astToCode)
 }
 
-//variables that are in scope of given variable
+//variables that are in scope of given variable(function,if)
 scopedvars = {};
 //variables given as argument of a function
 funcargs = {};
 //variables decalred inside scope of a function
 funcvars = {};
 //to differentiate anonymous functions, ast does not do automatically.
+refac_funcs = {};
+cbcount = 0;
 var anon_count = 0;
 
 async function readfilee(file,cb){
 	fs.readFile(file, "utf-8", function (err,data){
 		cb(data);
-	})
-}
-var writefile = function(file,data,cb){
-	fs.writeFile(file,data,function(err){
-		cb();
 	})
 }
 
@@ -66,7 +63,8 @@ var getcount = function(data){
 	var count =0;
 	for(var key in data){
 		if(data.hasOwnProperty(key)){
-			if(data[key]["_class"]=="AST_Var" && data[key]["definitions"][0]["value"]["_class"]=="AST_Function"){
+			if(data[key]["_class"]=="AST_Var" 
+				&& data[key]["definitions"][0]["value"]!=null&& data[key]["definitions"][0]["value"]["_class"]=="AST_Function"){
 				count++;
 			}
 			if(data[key]["_class"]=="AST_SimpleStatement"){
@@ -79,7 +77,8 @@ var getcount = function(data){
 					})
 				}
 			}
-			if(data[key]["_class"]=="AST_Var" && data[key]["definitions"][0]["value"]["_class"]=="AST_Call"){
+			if(data[key]["_class"]=="AST_Var" 
+				&& data[key]["definitions"][0]["value"]!=null&& data[key]["definitions"][0]["value"]["_class"]=="AST_Call"){
 				if("args" in  data[key]["definitions"][0]["value"]){
 					templist = data[key]["definitions"][0]["value"]["args"];
 					templist.forEach(function(i){
@@ -94,6 +93,11 @@ var getcount = function(data){
 			}
 			if(data[key]['_class']=='AST_For'){
 				count++;
+			}
+			if(data[key]['_class']=='AST_If'){
+				count++;
+				if(data[key]['alternative']!=null)
+					count++;
 			}
 		}
 	}
@@ -115,7 +119,7 @@ async function printify(data, scope, list, indent,cb){
 		var check = 0;
 		for(var key in data){
 			if(data.hasOwnProperty(key)){
[…]

### 2019-05-07 latex-template/paper.tex
testing, handle error in npm/cli file
Updated abstract

@@
 However, a poor understanding of callbacks can result in many complexities such as nested callbacks (also referred to as callback hell).
-Another problem that nested callbacks can cause is lose of benefit of asynchrony since execution of program becomes linear when independent functions are nested into callbacks of other function calls.
-We present a tool developed in JavaScript that checks for independent instructions inside callbacks and refactors them outside of callbacks.
+Another problem that nested callbacks can cause is loss of the benefit of asynchrony since execution of program becomes linear when independent functions are nested into callbacks of other function calls.
+One major factor which causes the loss of asynchrony, are instructions that are being used within a callback but can be executed before the callback is actually called.
+We present a technique that analyzes code and is able to suggest refactorable instructions within callbacks based upon where these instructions are declared and used.
+We tested our tool on multiple JavaScript files.
 \end{abstract}
@@
 	\item Implementation
+	\item Testing
 	\item Limitations and Challenges

### 2019-05-09 latex-template/paper.tex
added examples of code

@@
 }
-\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
+\author{\IEEEauthorblockN{Ammar Tahir}
 \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
@@
 \and
-\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
+\IEEEauthorblockN{Sheikh Abdul Mannan}
 \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
@@
 \and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
+\IEEEauthorblockN{Junaid Haroon Siddiqui}
 \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
@@
 \subsection{Decision based refactoring}
+
+\begin{figure}[htbp]
+	\includegraphics[scale=0.5]{not-refactorable-example.png}
+	\caption{An example where instruction (at line number 2) is not refactorable}
+	\label{fig}
+\end{figure}
+
+\begin{figure}[htbp]
+	\includegraphics[scale=0.5]{refactorable-example.png}
+	\caption{An example where instruction (at line number 3) is refactorable}
+	\label{fig}
+\end{figure}
+
 After we have execution context and we know scopes of different variables, we can now make decisions about what instructions are refactorable.
@@
 In this case, instruction is safe to be refactored.}
-	\item{\textbf{Instruction depends upon function argument:}Since callbacks may include instructions that are dependent upon arguments of main function, we should not refactor these instructions out of function.}
+	\item{\textbf{Instruction depends upon function argument:}Since callbacks may include instructions that are dependent upon arguments of main function, we should not refactor these instructions out of function.
+Figure 3 shows another version of code from figure 1 where line 2 is not refactorable now.}
 	\item{\textbf{Instructions depend upon variables declared in scope of parent function:}
-		In this case, such an instruction will be safe to be refactored.}
+		In this case, such an instruction will be safe to be refactored. Consult figure 4, where line number 2 is refactorable now because it has been declared in scope outside of containing function.}
 	\item{\textbf{Instruction depends on a variable declared within the scope of function:}

### 2019-05-09 latex-template/paper.tex
update testing results

@@
 \section{Testing}
+We tested our results on multiple JavaScript files from some npm modules as well as a few self-written files.
+Due to certain limitations we got a large number of false positives, however, we figured that by handling more cases we could get rid of these false positives.
+On a total of 9 JavaScript files with a total 2239 lines of code, our implementation of proposed technique suggested a total of 1472 instructions that could be refactored.
+This should be noted that an instruction can be counted towards being refactored more than once when it is nested into callbacks multiple times.
+In fact, the JavaScript files we explicitly took up for testing were those which had a large number of nested callbacks with a significant number of these callbacks being anonymous functions.
+We picked files of multiple lengths varying from tens of lines of code to about 1000 lines of code.
+Maximum number of refactoring suggestion we got were 850 for a file with 980 lines of code.
+Most common types of false positives were:  function call with a value instead of placeholder variable, duplicate names in nested callbacks and some instructions that user expects execute at certain place for example socket.close() or console,log().
+Although,a very significant proportion of suggestions we got from our implementation were false positives, we expect results to improve reasonably once more corner cases are catered.
+
 \section{Limitations and Challenges}

### 2019-05-09 latex-template/paper.tex
Update paper.tex

@@
 
-\title{Paper Title*\\
+\title{RefactorMyCallbacks : An automation to refactor
+instructions from within callbacks in JavaScript\\
 %{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
@@
 \author{\IEEEauthorblockN{Ammar Tahir}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
+\IEEEauthorblockA{\textit{Computer Science Department} \\
+\textit{LUMS}\\
+Lahore, Pakistan \\
+20100212@lums.edu.pk}
 \and
 \IEEEauthorblockN{Sheikh Abdul Mannan}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
+\IEEEauthorblockA{\textit{Computer Science Department} \\
+\textit{LUMS}\\
+Lahore, Pakistan \\
+20100261@lums.edu.pk}
 \and
 \IEEEauthorblockN{Junaid Haroon Siddiqui}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
+\IEEEauthorblockA{\textit{Computer Science Department} \\
+\textit{LUMS}\\
+Lahore, Pakistan \\
+junaid.siddiqui@lums.edu.pk}
 }
@@
 Rest of the articles is divided into following order:
-\begin{itemize}
+\begin{enumerate}
 	\item Methodology
@@
 
-\end{itemize}
+\end{enumerate}
 
@@
 Our solution mainly consists of 3 major parts:
-\begin{itemize}
+\begin{enumerate}
 	\item AST extraction
@@
 	\item Decision based refactoring
-\end{itemize}
+\end{enumerate}
 \subsection{AST extraction}
@@
 
-\begin{figure}[htbp]
+\begin{figure}[t]
 	\includegraphics[scale=0.5]{code-execcon-extract.png}
@@
 \subsection{Decision based refactoring}
-
-\begin{figure}[htbp]
-	\includegraphics[scale=0.5]{not-refactorable-example.png}
-	\caption{An example where instruction (at line number 2) is not refactorable}
-	\label{fig}
-\end{figure}
-
-\begin{figure}[htbp]
-	\includegraphics[scale=0.5]{refactorable-example.png}
-	\caption{An example where instruction (at line number 3) is refactorable}
-	\label{fig}
-\end{figure}
 
@@
 
-\begin{figure}[htbp]
+\begin{figure}[t]
+	\includegraphics[scale=0.5]{not-refactorable-example.png}
+	\caption{An example where instruction (at line number 2) is not refactorable}
+	\label{fig}
+\end{figure}
+
+\begin{figure}[t]
+	\includegraphics[scale=0.5]{refactorable-example.png}
+	\caption{An example where instruction (at line number 3) is refactorable}
+	\label{fig}
+\end{figure}
+\begin{figure}[t]
 	\includegraphics[scale=0.5]{code-decision-refactor.png}
